Online Supplement to "Demographic costs of sexually antagonistic selection in partially selfing populations" \\ \textit{The~American~Naturalist}

### 2021-06-04 doc/Supplements/SupplementaryMaterial.tex
Anonymized github links
This commit adds anonymized GitHub links to the main and supp.
documents.

Because these coexistence conditions contain the stable stage specific frequencies on the boundaries, $\hat{\mbf{p}}_{X,AA}$, and $\hat{\mbf{p}}_{S,aa}$, finding an analytical expression in terms of the model parameters (i.e., a closed form solution),  is in general a non trivial task. We therefore used numerical techniques as described in the main text to identify invasion and extinction thresholds, which could then be used to define regions of demographically viable polymorphism across $s_f \times s_m$ parameter space. All computer code necessary to reproduce the results are available at \url{https://github.com/colin-olito/SA-Hermaphrodites-wDemography}.

>>>>

Because these coexistence conditions contain the stable stage specific frequencies on the boundaries, $\hat{\mbf{p}}_{X,AA}$, and $\hat{\mbf{p}}_{S,aa}$, finding an analytical expression in terms of the model parameters (i.e., a closed form solution),  is in general a non trivial task. We therefore used numerical techniques as described in the main text to identify invasion and extinction thresholds, which could then be used to define regions of demographically viable polymorphism across $s_f \times s_m$ parameter space. All computer code necessary to reproduce the results are available at \url{https://anonymous.4open.science/r/SA-Hermaphrodites-wDemography-BF66}.%\url{https://github.com/colin-olito/SA-Hermaphrodites-wDemography}.
